---
title: "research-day-2026"
output: html_document
date: "2026-04-10"
---
      ~ Research Day 2026! ~

1) LIBRARIES, FILES, POSTER DATAFRAME! 
```{r setup, include=TRUE}

### LIBRARIES USED ###
library(dplyr)
library(tidyr)
library(ggcorrplot)
library(lubridate)
library(mgcv)
library(purrr)
library(insight)
library(patchwork)
library(dominanceanalysis)
library(LNCDR)
library(lme4)
library(lmerTest)
library(partR2)
library(tidyverse)
library(ggplot2)
library(gratia)
library(tibble)
library(MetBrewer) # pretty colors 
library(ggplotify)

setwd("/Users/angelamartinez/Desktop/PROJECTS/HPC MYELIN") #
whoqol_myelin_day <- read.csv("whoqol_myelin_day.csv")
whoqol_items <- read.csv("whoqol_items.csv")
dts_df <- read.csv("dts_df_am (1).csv")

# RENAME #
whoqol_items <- whoqol_items %>% rename(mprage.sesno = mp2rage.session_number)

research.2026 <- whoqol_myelin_day %>% left_join(whoqol_items %>% select(lunaid, mprage.sesno, whoqol8, whoqol9, whoqol12, whoqol13, whoqol14, whoqol23, whoqol24, whoqol25), by = c("lunaid", "mprage.sesno")) 

# REMOVING N/As AND DUPLICATES #
# research.2026 <- research.2026 %>% filter(!if_all(c(q1_overall, q2_health, D1_physical, D2_psych, D3_social, D4_env, whoqol8, whoqol9, whoqol12, whoqol13, whoqol14, whoqol23, whoqol24, whoqol25),is.na))

research.2026 <- research.2026 %>% filter(!if_all(c(q1_overall, q2_health, D1_physical, D2_psych, D3_social, D4_env),is.na))

research.2026 <- research.2026 %>% distinct(lunaid, mprage.sesno, .keep_all = TRUE) %>% tidyr::fill(ADI_NATRANK, .direction = "downup")

# TOTAL SAMPLE #
research.2026.distribution <- research.2026 %>% count(mprage.sesno, name = "n_subs")

## RESEARCH.2026 SUMMARY ##
# 1 -- 140
# 2 -- 64
# 3 -- 20

```

FOR CONTEXT: IS SUBJECTIVE AND OBJECTIVE ENVIRONMENT CAPUTRING SIMILAR OR DIFFERENT THINGS? 
```{r message=FALSE, warning=FALSE}
### WHOQOL-ENV IS COMPLEMENTARY TO ADI USING LINEAR MIXED MODEL ###
lmixed <- lmer(D4_env ~ ADI_NATRANK + age + sex + (1 | lunaid), data = research.2026)
summary(lmixed)

### CALCULATE THE STRENGTH USING PARTIAL R SQUARED ###
  # how much variance in whoqol is explained by ADI ? #
  # R2_TYPE DIFFERENCES #
    # NOTE: marginal parses through random effects WHILE conditional includes variance explained by random effect #
partialR <- partR2(lmixed, partvars = c("age", "sex", "ADI_NATRANK"), data = research.2026, R2_type = "marginal")
partialR
# OUTPUT: 4.5%, however, supports idea that significantly related but capturing different things #

### DOMINANCE ANALYSIS - ADI AS A PREDICTOR ### -- WHICH QUESTIONS ARE DRIVING THE RELATIONSHIP WHOQOL & ADI ENV ??
env_items_df <- research.2026 %>% rename(
    Safety = whoqol8,
    Physical_Environment = whoqol9,
    Financial_Resources = whoqol12,
    Information_Available = whoqol13,
    Leisure_Opportunities = whoqol14,
    Home_Environment = whoqol23,
    Health_Services = whoqol24,
    Transport = whoqol25)

EnvADI.DA.model <- lm(ADI_NATRANK ~ D4_env + Safety + Physical_Environment + Financial_Resources + Information_Available + Leisure_Opportunities + Home_Environment + Health_Services + Transport, data = env_items_df)

EnvADI.DA <- dominanceAnalysis(EnvADI.DA.model)
# summary(EnvADI.DA)

plot(EnvADI.DA)
plot(EnvADI.DA) + coord_flip() 

### Financial_Resources -- item 12 -- has the most weight out of environmental domain ###
```

AIM 1: DEVELOPMENTAL TRAJECTOIES OF MYELINATION - SIMILAR TO DANS 2025 AND ETC. 
```{r}
# COMPUTING AVERAGES #
research.2026$hipp_head_R1_avg  <- (research.2026$lh_head_R1 + research.2026$rh_head_R1) / 2
research.2026$hipp_body_R1_avg  <- (research.2026$lh_body_R1 + research.2026$rh_body_R1) / 2
research.2026$hipp_tail_R1_avg  <- (research.2026$lh_tail_R1 + research.2026$rh_tail_R1) / 2
research.2026$hipp_whole_R1_avg <- (research.2026$lh_hippocampus_R1 + research.2026$rh_hippocampus_R1) / 2

### AGE ON HPC ###
# WHOLE #
ageWHOLEHPC <- gam(hipp_whole_R1_avg ~ s(age, k = 4) + sex + s(lunaid, bs = "re"), method = "REML", data = research.2026)
summary(ageWHOLEHPC)

# RIGHT HEM #
ageRIGHTHEM <- gam(rh_hippocampus_R1 ~ s(age, k = 4) + sex + s(lunaid, bs = "re"), method = "REML", data = research.2026)
summary(ageRIGHTHEM)

# LEFT HEM #
ageLEFTHEM <- gam(lh_hippocampus_R1 ~ s(age, k = 4) + sex + s(lunaid, bs = "re"), method = "REML", data = research.2026)
summary(ageLEFTHEM)




```

AIM 2: ARE WHOQOL AND ADI RELATED TO HPC R1 INDEPENDENTLY? 
```{r message=FALSE, warning=FALSE}

### ADI PREDICTING R1 WHOLE HPC ###  
# WHOLE HPC #
adigam <- gam(hipp_whole_R1_avg ~ ADI_NATRANK + s(age, k = 4) + sex + s(lunaid, bs = "re"), method = "REML", data = research.2026)
summary(adigam)

# RIGHT HEM #
adigam.rh <- gam(rh_hippocampus_R1 ~ ADI_NATRANK + s(age, k = 4) + sex + s(lunaid, bs = "re"), method = "REML", data = research.2026)
summary(adigam.rh)

# LEFT HEM #
adigam.lh <- gam(lh_hippocampus_R1 ~ ADI_NATRANK + s(age, k = 4) + sex + s(lunaid, bs = "re"), method = "REML", data = research.2026)
summary(adigam.lh)

### WHOQOL-ENV PREDICTING R1 HPC ### 
# WHOLE #
whoqolgam <- gam(hipp_whole_R1_avg ~ D4_env + s(age, k = 4) + sex + s(lunaid, bs = "re"), method = "REML", data = research.2026)
summary(whoqolgam)

# RIGHT HEM #
whoqolgam.rh <- gam(rh_hippocampus_R1 ~ D4_env + s(age, k = 4) + sex + s(lunaid, bs = "re"), method = "REML", data = research.2026)
summary(whoqolgam.rh)

# LEFT HEM #
whoqolgam.lh <- gam(lh_hippocampus_R1 ~ D4_env + s(age, k = 4) + sex + s(lunaid, bs = "re"), method = "REML", data = research.2026)
summary(whoqolgam.lh)

### Financial Resources (ITEM 12) PREDICTING R1 WHOLE HPC ###
# WHOLE #
FRgam <- gam(hipp_whole_R1_avg ~ whoqol12 + s(age, k = 4) + sex + s(lunaid, bs = "re"), method = "REML", data = research.2026)
summary(FRgam)

# RIGHT HEM #
FRgam.rh <- gam(rh_hippocampus_R1 ~ whoqol12 + s(age, k = 4) + sex + s(lunaid, bs = "re"), method = "REML", data = research.2026)
summary(FRgam.rh)

# LEFT HEM #
FRgam.lh <- gam(lh_hippocampus_R1 ~ whoqol12 + s(age, k = 4) + sex + s(lunaid, bs = "re"), method = "REML", data = research.2026)
summary(FRgam.lh)


```

EXPLORATORY: DOES SUBJECTIVE WELL-BEING OF ENVIRONMENT MODERATE THE ASSOCIATION BETWEEN ADI & R1 ?
```{r message=FALSE, warning=FALSE}
### MODERATOR ### 
# WHOLE #
whoqolmod <- gam(hipp_whole_R1_avg ~ ADI_NATRANK*D4_env + s(age, k = 4) + sex + s(lunaid, bs = "re"), method = "REML", data = research.2026)
summary(whoqolmod)

# RIGHT #
whoqolmod.rh <- gam(rh_hippocampus_R1 ~ ADI_NATRANK*D4_env + s(age, k = 4) + sex + s(lunaid, bs = "re"), method = "REML", data = research.2026)
summary(whoqolmod.rh)

# LEFT #
whoqolmod.lh <- gam(lh_hippocampus_R1 ~ ADI_NATRANK*D4_env + s(age, k = 4) + sex + s(lunaid, bs = "re"), method = "REML", data = research.2026)
summary(whoqolmod.lh)

```

    ~ Distress Tolerance! ~
NEW TOTAL SAMPLE -- ADDING DISTRESS TOLERANCE TO THE MIX AND CREATING A SEPARATE DATAFRAME 
```{r message=FALSE, warning=FALSE}
research.2026.DTS <- research.2026 %>% left_join(dts_df %>% select(lunaid, visitno, DTS_Tolerance:DTS_Total), by = c("lunaid", "visitno")) 

research.2026.DTS <- research.2026.DTS %>% filter(!if_all(c(DTS_Tolerance, DTS_Absorb, DTS_Appraise, DTS_Regulate, DTS_Total),is.na))

research.2026.DTS <- research.2026.DTS %>% distinct(lunaid, visitno, .keep_all = TRUE)

# TOTAL SAMPLE #
research.2026.DTS.distribution <- research.2026.DTS %>% count(visitno, name = "n_subs")

## RESEARCH.2026.DTS SUMMARY ##
# 1 -- 118
# 2 -- 60
# 3 -- 30

```

NEXT QUESTIONS: DOES LOW TOLERANCE TO STRESS IMPACT INDIVIDUAL'S PERCEIVED QUALITY OF THEIR ENVIRONMENT? HOW DOES THIS IMPACT RELATIONSHIP TO R1? 

EXPLORATORY: DISTRESS TOLERANCE -- A PSYCHOLOGICAL CONSTRUCT THAT TAPS INTO ADAPTABILITY
DOES DT MODERATE THE ASSOCIATION BETWEEN ADI / WHOQOL-ENV & R1, RESPECTIVELY? 
```{r message=FALSE, warning=FALSE}

### DOMINANCE ANALYSIS -- DTS_APPRAISE SHOWED MOST VARIANCE ###
EnvDTS.DA.model <- lm(D4_env ~ DTS_Total + DTS_Absorb + DTS_Appraise + DTS_Tolerance + DTS_Regulate, data = research.2026.DTS)
EnvDTS.DA <- dominanceAnalysis(EnvDTS.DA.model)
# summary(EnvDTS.DA)
plot(EnvDTS.DA)
plot(EnvDTS.DA) + coord_flip() 

### DTS --> WHOQOL ENV ###
dtswhoqol <- gam(D4_env ~ DTS_Total + s(age, k = 4) + sex + s(lunaid, bs = "re"), method = "REML", data = research.2026.DTS)
summary(dtswhoqol)

### LOWER VS HIGHER DTS SCORES ###
# Range for Total: 3 - 18 #
# cut off point: 8 #
### NOTE: higher scores means lower distress Tolerance ###
low <- research.2026.DTS %>% filter(DTS_Total >= 8)
high <- research.2026.DTS %>% filter(DTS_Total <= 8)

### AREA DEPRIVATION INDEX -- FINDINGS FOR RESEARCH DAY POSTER ###
# WHOLE #
ADI.DTS.LOW.whole <- gam(hipp_whole_R1_avg ~ ADI_NATRANK*DTS_Total + s(age, k = 4) + sex + s(lunaid, bs = "re"), method = "REML", data = low)
summary(ADI.DTS.LOW.whole)

ADI.DTS.HIGH.whole <- gam(hipp_whole_R1_avg ~ ADI_NATRANK*DTS_Total + s(age, k = 4) + sex + s(lunaid, bs = "re"), method = "REML", data = high)
summary(ADI.DTS.HIGH.whole)

ADI.DTS.MODERATION <- gam(hipp_whole_R1_avg ~ ADI_NATRANK*DTS_Total + s(age, k = 4) + sex + s(lunaid, bs = "re"), method = "REML", data = research.2026.DTS)
summary(ADI.DTS.MODERATION)

### etc. ###
# RIGHT #
ADI.DTS.LOW.right <- gam(rh_hippocampus_R1 ~ ADI_NATRANK*DTS_Total + s(age, k = 4) + sex + s(lunaid, bs = "re"), method = "REML", data = low)
summary(ADI.DTS.LOW.right)

ADI.DTS.HIGH.right <- gam(rh_hippocampus_R1 ~ ADI_NATRANK*DTS_Total + s(age, k = 4) + sex + s(lunaid, bs = "re"), method = "REML", data = high)
summary(ADI.DTS.HIGH.right)

# LEFT #
ADI.DTS.LOW.left <- gam(lh_hippocampus_R1 ~ ADI_NATRANK*DTS_Total + s(age, k = 4) + sex + s(lunaid, bs = "re"), method = "REML", data = low)
summary(ADI.DTS.LOW.left)

ADI.DTS.HIGH.left <- gam(lh_hippocampus_R1 ~ ADI_NATRANK*DTS_Total + s(age, k = 4) + sex + s(lunaid, bs = "re"), method = "REML", data = high)
summary(ADI.DTS.HIGH.left)

### D4 ENVIRONMENTAL DOMAIN ###
# WHOLE #
ENV.DTS.LOW.whole <- gam(hipp_whole_R1_avg ~ D4_env*DTS_Total + s(age, k = 4) + sex + s(lunaid, bs = "re"), method = "REML", data = low)
summary(ENV.DTS.LOW.whole)

ENV.DTS.HIGH.whole <- gam(hipp_whole_R1_avg ~ D4_env*DTS_Total + s(age, k = 4) + sex + s(lunaid, bs = "re"), method = "REML", data = high)
summary(ENV.DTS.HIGH.whole)

ENV.DTS.Moderation <- gam(hipp_whole_R1_avg ~ D4_env*DTS_Total + s(age, k = 4) + sex + s(lunaid, bs = "re"), method = "REML", data = research.2026.DTS)
summary(ENV.DTS.HIGH.whole)

# RIGHT #
ENV.DTS.LOW.right <- gam(rh_hippocampus_R1 ~ D4_env*DTS_Total + s(age, k = 4) + sex + s(lunaid, bs = "re"), method = "REML", data = low)
summary(ENV.DTS.LOW.right)

ENV.DTS.HIGH.right <- gam(rh_hippocampus_R1 ~ D4_env*DTS_Total + s(age, k = 4) + sex + s(lunaid, bs = "re"), method = "REML", data = high)
summary(ENV.DTS.HIGH.right)

# LEFT #
ENV.DTS.LOW.left <- gam(lh_hippocampus_R1 ~ D4_env*DTS_Total + s(age, k = 4) + sex + s(lunaid, bs = "re"), method = "REML", data = low)
summary(ENV.DTS.LOW.left)

ENV.DTS.HIGH.left <- gam(lh_hippocampus_R1 ~ D4_env*DTS_Total + s(age, k = 4) + sex + s(lunaid, bs = "re"), method = "REML", data = high)
summary(ENV.DTS.HIGH.left)

### HISTOGRAM: TOTAL DISTRESS TOLERANCE ACROSS AGE GROUPS ###
dts_long2 <- research.2026.DTS %>%
  select(lunaid, visitno, age, DTS_Total) %>%
  pivot_longer(cols = DTS_Total, names_to = "Domain", values_to = "Score") %>%
  mutate(age_group = cut(age,
                         breaks = c(0, 16, 20, 24, 33), 
                         labels = c("10-15", "16-19", "20-23", "24-32")))

ggplot(dts_long2, aes(x = Score, fill = age_group)) +
  geom_histogram(position = "identity", alpha = 0.6, bins = 30) +
  facet_wrap(~ Domain, scales = "free") +
  labs(title = "DTS Total Scores by Age Group",
       x = "Domain Total",
       y = "Count") +
  theme_minimal()
        
    
### HISTOGRAM: DTS DOMAIN SCORES BY AGE GROUP ###
dts_long <- research.2026.DTS %>%
  select(lunaid, visitno, age, DTS_Tolerance:DTS_Total) %>%
  pivot_longer(cols = DTS_Tolerance:DTS_Total, names_to = "Domain", values_to = "Score") %>%
  mutate(age_group = cut(age,
                         breaks = c(0, 16, 20, 24, 33), 
                         labels = c("10-15", "16-19", "20-23", "24-32")))

ggplot(dts_long, aes(x = Score, fill = age_group)) +
  geom_histogram(position = "identity", alpha = 0.6, bins = 30) +
  facet_wrap(~ Domain, scales = "free") +
  labs(title = "DTS Domain Scores by Age Group",
       x = "Domain Score",
       y = "Count") +
  theme_minimal()

### GREATER DISTRESS TOLERANCE IS HIGHLY CORRELATED TO PERCEIVED ENVIRONMENTLA QUALITY ###

##### LOOKING AT ALL THE DOMAINS FOR OBJECTIVE AND PERCEIVED ENVIRONMENTAL #####
# AREA DEPRIVATION INDEX #
ADI.DTS.TOLERANCE <- gam(hipp_whole_R1_avg ~ s(age, k = 4) + sex + s(lunaid, bs = "re") + ADI_NATRANK*DTS_Tolerance, method = "REML", data = research.2026.DTS)
summary(ADI.DTS.TOLERANCE)

ADI.DTS.ABSORPTION <- gam(hipp_whole_R1_avg ~ s(age, k = 4) + sex + s(lunaid, bs = "re") + ADI_NATRANK*DTS_Absorb, method = "REML", data = research.2026.DTS)
summary(ADI.DTS.ABSORPTION)

ADI.DTS.APPRAISE <- gam(hipp_whole_R1_avg ~ s(age, k = 4) + sex + s(lunaid, bs = "re") + ADI_NATRANK*DTS_Appraise, method = "REML", data = research.2026.DTS)
summary(ADI.DTS.APPRAISE)

ADI.DTS.REGULATE <- gam(hipp_whole_R1_avg ~ s(age, k = 4) + sex + s(lunaid, bs = "re") + ADI_NATRANK*DTS_Regulate, method = "REML", data = research.2026.DTS)
summary(ADI.DTS.REGULATE)

ADI.DTS.TOTAL <- gam(hipp_whole_R1_avg ~ s(age, k = 4) + sex + s(lunaid, bs = "re") + ADI_NATRANK*DTS_Total, method = "REML", data = research.2026.DTS)
summary(ADI.DTS.TOTAL)

# WHOQOL BREF #
QOL.DTS.TOLERANCE <- gam(hipp_whole_R1_avg ~ s(age, k = 4) + sex + s(lunaid, bs = "re") + D4_env*DTS_Tolerance, method = "REML", data = research.2026.DTS)
summary(QOL.DTS.TOLERANCE)

QOL.DTS.ABSORPTION <- gam(hipp_whole_R1_avg ~ s(age, k = 4) + sex + s(lunaid, bs = "re") + D4_env*DTS_Absorb, method = "REML", data = research.2026.DTS)
summary(QOL.DTS.ABSORPTION)

QOL.DTS.APPRAISE <- gam(hipp_whole_R1_avg ~ s(age, k = 4) + sex + s(lunaid, bs = "re") + D4_env*DTS_Appraise, method = "REML", data = research.2026.DTS)
summary(QOL.DTS.APPRAISE)

QOL.DTS.REGULATE <- gam(hipp_whole_R1_avg ~ s(age, k = 4) + sex + s(lunaid, bs = "re") + D4_env*DTS_Regulate, method = "REML", data = research.2026.DTS)
summary(QOL.DTS.REGULATE)

QOL.DTS.TOTAL <- gam(hipp_whole_R1_avg ~ s(age, k = 4) + sex + s(lunaid, bs = "re") + D4_env*DTS_Total, method = "REML", data = research.2026.DTS)
summary(QOL.DTS.TOTAL)

#### CORRELATION TESTS FOR WHOQOL AND DTS ###
cor.test(research.2026.DTS$D4_env, research.2026.DTS$DTS_Total)
cor.test(research.2026.DTS$D4_env, research.2026.DTS$DTS_Tolerance)
cor.test(research.2026.DTS$D4_env, research.2026.DTS$DTS_Absorb)
cor.test(research.2026.DTS$D4_env, research.2026.DTS$DTS_Appraise)
cor.test(research.2026.DTS$D4_env, research.2026.DTS$DTS_Regulate)

```

FINAL RESEARCH DAY FIGURES
```{r}
### COLOR PALETTE - RED WINE SUMMER VIBES #
redwine <- c(
  "#F4C3CF", #1
  "#E9A8B6", #2
  "#C45A67", #3
  "#9A2E3A", #4
  "#5A1A22"  #5
)

### GLOBAL THEME FOR CONSISTENCY ACROSS ALL FIGS ###
theme_set(
  theme_classic(base_size = 16, base_family = "Times New Roman") +
    theme(
      plot.title = element_text(face = "bold"),
      axis.title = element_text(face = "bold")
    ))

### R1 INCREASES NON-LINEARLY WITHIN THE ADOLESCENT HIPPOCAMPUS ###
# raw data visualization -- AIM 1: DEVELOPMENTAL #
# WHOLE HIPP #
ggplot(research.2026, aes(x = age, y = hipp_whole_R1_avg)) +
  geom_point(alpha = 0.35, color = redwine[5]) +
  geom_smooth(
    method = "gam",
    formula = y ~ s(x, k = 4),
    color = redwine[5],
    fill = redwine[5],
    alpha = 0.2,
    linewidth = 1.2
  ) + labs(
    title = "Whole Hippocampus", x = "Age (years)", y = "R1 value")

# RIGHT HIPP #
ggplot(research.2026, aes(age, rh_hippocampus_R1)) +
  geom_point(alpha = 0.35, color = redwine[4]) +
  geom_smooth(
    method = "gam",
    formula = y ~ s(x, k = 4),
    color = redwine[4],
    fill = redwine[4],
    alpha = 0.2,
    linewidth = 1.2
  ) +
  labs(title = "Right Hippocampus", x = "Age (years)", y = "R1 value")

# LEFT HIPP #
ggplot(research.2026, aes(age, lh_hippocampus_R1)) +
  geom_point(alpha = 0.35, color = redwine[3]) +
  geom_smooth(
    method = "gam",
    formula = y ~ s(x, k = 4),
    color = redwine[3],
    fill = redwine[3],
    alpha = 0.2,
    linewidth = 1.2
  ) +
  labs(title = "Left Hippocampus", x = "Age (years)", y = "R1 value")

### AREA DEPRIVATION INDEX AND WHO QUALITY OF LIFE ENVIRONMENT MEASRES CAPTURE BOTH SHARED AND UNIQUE VARIANCES IN YOUTHS' ENVIRONMENT ###
# contextualization #

# WHOQOL-ENV distribution #
p_env <- ggplot(research.2026, aes(D4_env)) +
  geom_histogram(binwidth = 5, fill = redwine[4], color = "black", linewidth = 0.4) +
  labs(x = "WHOQOL-ENV Score", y = "")
p_env

  
# ADI distribution #
p_adi <- ggplot(research.2026, aes(ADI_NATRANK)) +
  geom_histogram(binwidth = 5, fill = redwine[3], color = "black", linewidth = 0.4) +
  labs(x = "ADI Score", y = "Number of Participants")
p_adi

p_adi | p_env 

# DOMINANCE ANALYSIS FIGURE CREATED OUTSIDE OF R (BARCHARTS) #

### WHOQOL ENV and ADI CORRELATION GRAPH ###
ggplot(research.2026, aes(ADI_NATRANK, D4_env)) +
  geom_point(alpha = 0.5, color = redwine[4]) +
  geom_smooth(method = "lm", color = "black", se = TRUE) +
  labs(x = "Area Deprivation Index", y = "WHOQOL-ENV")

### GREATER ENVIRONMENTAL DEPRIVATION IS ASSOCIATED WITH LOWER HPC-R1 ###
# Raw visualization of ADI -> HPC R1 #
ggplot(research.2026, aes(ADI_NATRANK, hipp_whole_R1_avg)) +
  geom_point(alpha = 0.5, color = redwine[3]) +
  geom_smooth(method = "lm", color = "black", se = TRUE) +
  labs(x = "ADI Scores", y = "R1 value")

# Raw visualization of WHOQOL-ENV -> HPC R1 #
ggplot(research.2026, aes(D4_env, hipp_whole_R1_avg)) +
  geom_point(alpha = 0.5, color = redwine[4]) +
  geom_smooth(method = "lm", color = "black", se = TRUE) +
  labs(x = "WHOQOL-ENV Scores", y = "R1 value")

### DISTRESS TOLERANCE WAS ASSOCIATED WITH PERCEIVED ENVRIONMENTAL QUALITY BUT DOES NOT MODERATE ENVIRONMENT-R1 ASSOCIATION ###

## TOLERANCE ##
ggplot(research.2026.DTS, aes(DTS_Tolerance, D4_env)) +
  geom_point(alpha = 0.8, color = redwine[2]) +
  geom_smooth(method = "lm", se = TRUE, color = redwine[4], linewidth = 1.5) +
  labs(x = "Tolerance Domain Score", y = "Perceived Environmental Quality")

## APPRAISAL ##
ggplot(research.2026.DTS, aes(DTS_Appraise, D4_env)) +
  geom_point(alpha = 0.8, color = redwine[2]) +
  geom_smooth(method = "lm", se = TRUE, color = redwine[4], linewidth = 1.5) +
  labs(x = "Appraisal Domain Score", y = "Perceived Environmental Quality")

## ABSORPTION ##
ggplot(research.2026.DTS, aes(DTS_Absorb, D4_env)) +
  geom_point(alpha = 0.8, color = redwine[2]) +
  geom_smooth(method = "lm", se = TRUE, color = redwine[4], linewidth = 1.5) +
  labs(x = "Absorption Domain Score", y = "Perceived Environmental Quality")

## REGULATION ##
ggplot(research.2026.DTS, aes(DTS_Regulate, D4_env)) +
  geom_point(alpha = 0.8, color = redwine[2]) +
  geom_smooth(method = "lm", se = TRUE, color = redwine[4], linewidth = 1.5) +
  labs(x = "Regulation Domain Score", y = "Perceived Environmental Quality")

```

